\documentclass[11pt,a4paper]{moderncv}

\usepackage{enumitem}
% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[T1]{fontenc}
\usepackage{lmodern}
% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage[english]{babel}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\footnotesize } % other info in "inner" position of footer line

%number is section
%\newcounter{secnumber}
%\renewcommand\sectionstyle[1]{{%
		%  \refstepcounter{secnumber}%
		%  \sectionfont
		%  \textcolor{color1}{\thesecnumber~#1}%
		%}}

% personal data
\firstname{\Huge Sim\'on Emmanuel}
\familyname{Guti\'errez Brida}
\title{Curriculum Vitae} 
%\address{<Address Street>}{<Addres Place>}
\mobile{+549 (358) 4396 444}
\phone{+549 (358) 4676 235}
%\fax{<Fax number>}
\email{sgutierrez@dc.exa.unrc.edu.ar}
\homepage{http://saiema.github.io/}
\social[orcid]{0000-0003-3115-2739}

%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[100pt]{pict.JPG}
%\photo[84pt]{foto.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"Success is the ability to go from failure to failure without losing your enthusiasm." -- Winston Churchill}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{wasysym}

\begin{document}
	\maketitle
	
	%Section
	\section*{Personal Information}
	%\cvcomputer{Nombre:}{Renzo Degiovanni}{D.N.I:}{32705627}
	%\cvline{}{Lugar de Nacimiento: R\'io Cuarto, C\'ordoba, Argentina}
	%\cvcomputer{Fecha y Lugar de Nacimiento:}{10/04/1987}{Estado Civil:}{Uni\'on de Hecho}
	%\cvcomputer{Lugar de Nacimiento:}{R\'io Cuarto, C\'ordoba, Argentina}{N\'umeros de Hijos:}{1}
	%\cvcomputer{Fecha de Nacimiento:}{10/04/1987}{Lugar de Nacimiento:}{R\'io Cuarto, C\'ordoba, Argentina}
	%\cvcomputer{Estado Civil:}{Uni\'on de Hecho}{Hijos:}{1}
	%\cvcomputer{Domicilio:}{Avenida C\'ordoba 515}{Localidad:}{Las Acequias, C\'ordoba, Argentina}
	\begin{minipage}{9cm}
		\begin{itemize}
			\item Full Name: Guti\'errez Brida, Sim\'on Emmanuel
			\item City: R\'io Cuarto, C\'ordoba
			\item Citizenship: Argentine
		\end{itemize}
	\end{minipage}
	\begin{minipage}{9cm}
		%\begin{itemize}
		%\item Date of Birth: 14/10/1983
		%\item Place of Birth: Buenos Aires City
		%\end{itemize}
	\end{minipage}
	
	
	\section*{Education}
	\cventry{2014-2019}{PhD in Computer Science}{}{Facultad de Matem\'atica, Astronom\'ia y F\'isica, Universidad Nacional de C\'ordoba}{C\'ordoba, Argentina}{Title: Mutation of Navigational Expressions for Testing and Program Repair. Advisor: Aguirre Nazareno. Description: In this thesis we develop a new mutation operator targeted at navigational expressions. Our operator extends the traditional operators set allowing the representation of new defect types in the context of mutation testing. In the context of automatic program repair, our operator increases the repairability.}
	\cventry{2009-2014}{Licenciatura in Computer Science (5 years degree)}{}{Universidad Nacional de R\'io Cuarto}{R\'io Cuarto, C\'ordoba, Argentina}{}
	
	
	\section*{Fellowhips/Scholarships}
	\cventry{2019-2021}{Posdoctoral Fellowship}{}{Funded by Consejo Nacional de Investigaciones Cient\'ificas y T\'ecnicas (CONICET)}{}{}
	\cventry{2014-2019}{PhD Scholarship}{}{Funded by Consejo Nacional de Investigaciones Cient\'ificas y T\'ecnicas (CONICET)}{}{}
	\cventry{2012}{Scholarship for students in the last years of Information and Communication Technologies related University careers.}{}{Funded by Agencia Nacional de Promoci\'on Cient\'ifica y Tecnol\'ogica}{}{}
	\cventry{2011}{Scientific stimulation Scholarship.}{Allows undergrad students to get involved in research projects.}{Funded by Consejo Interuniversitario Nacional}{}{}
	
	\section*{Research projects}
	
	\subsection*{Funded Research Projects}
	\cventry{2019}{Improving software testing through automatic translation of test inputs to API calls.}{Granted by Ministerio de Ciencia y Tecnología.}{}{}{}
	
	\subsection*{Colaborator}
	\cventry{2016-2018}{Formal methods for Software Specification, Design, and Verification.}{PPI}{Granted by Secretaria de Ciencia y T\'ecnica, Universidad Nacional de R\'io Cuarto}{Project Director Dr. Nazareno Aguirre}{}
	
	\cventry{2012-2015}{Formal methods for Software Specification, Design, and Verification.}{PPI}{Granted by Secretaria de Ciencia y T\'ecnica, Universidad Nacional de R\'io Cuarto}{Project Director Dr. Nazareno Aguirre}{}
	
	\section*{Employment Background}
	\subsection*{Academic / Teaching positions}
	
	\cventry{August 2024- March 2025}{Teaching Assistant}{}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{February 2024- August 2025}{Senior Teaching Assistant}{}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}

	\cventry{March 2023- March 2024}{Lecturer}{Guangdong Technion-Israel Institute of Technology}{Shantou, Guangdong Province, China}{}{Teacher in charge of 2 courses in the first semester; Teacher in charge of 2 courses in the second semester; Teaching Assistant in charge of tutorials and workshops of one course in the second semester.}
	
	\cventry{April 2019- February 2023}{Teaching Assistant}{}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	
	\cventry{April 2018- Dicember 2018}{Teaching Assistant}{}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{August 2015- March 2017}{Teaching Assistant}{}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{2008-2012}{Student Teaching Assistant}{}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\subsection*{Research Positions}
	
	\cventry{April 2019- April 2021}{Posdoctorate at Universidad Nacional Río Cuarto}{Research tittle: Automatic reconstruction of Objects from APIs.}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{From 2019}{Junior Researcher at MFIS}{Formal Methods \& Software Engineering research group.}{Computer Science Department at Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{\url{https://mfis.dc.exa.unrc.edu.ar}}
	
	\cventry{2023}{accepted for Researcher at CONICET}{CONICET, work place at Computer Science Department at Universidad Nacional de Río Cuarto}{Río Cuarto, Córdoba, Argentina.}{}{}
	
	\subsection*{Industry}
	
	\cventry{November 2013- April 2014}{Intern developer \textit{C++} in image processing, and pattern recognition}{Yeti Media, California}{}{}{}
	
	\section*{Teaching experience}
	
	\cventry{Lecturer}{Guangdong Technion-Israel Institute of Technology at Shantou, Guangdong Province, China}{Lecturer in charge of preparing both theoretical and practical class materials; preparing exercises; project design; exam design and evaluation; and lecturer (in charge of theoretical classes, workshops and laboratories)}{Courses: Introduction to Systems Programming (104824), Computer Organization and Programming (104818), Digital Systems and Computer Structure (104952)}{}{}
	
	\cventry{T. Assistant}{Guangdong Technion-Israel Institute of Technology at Shantou, Guangdong Province, China}{Tutor in charge of workshops and laboratories}{Courses: Introduction to Computer Science M (104814)}{}{}
	
	\cventry{Senior T. Assistant}{University of Rio Cuarto, Argentina.}{Managing Lab classes; Assisting in exercises and projects design, testing, and evaluation; Exams question proposal; Additional course content (examples and wikis); Substitute lecturer when needed}{Courses: Introduction to Algorithms (3375)}{}{}
	
	\cventry{T. Assistant}{University of Rio Cuarto, Argentina.}{Managing Lab classes; Assisting in exercises and projects design, testing, and evaluation; Exams question proposal; Additional course content (examples and wikis)}{Courses: Advanced Programming (1948), Data Structures and Algorithms (3301/3325), Algorithms Design (3302/3326), Computability and Complexity (3307), Project (1998), Distributed and Outsourced Software Engineering (3339)}{}{}
	
	
	\cventry{Student T. A.}{University of Rio Cuarto, Argentina}{Managing Lab classes; Assisting in exercises and projects design, testing, and evaluation}{Courses: Introduction to Algorithms (3300), Computer architecture (1949), Advanced Programming (1948), Data Structures and Algorithms (3301/3325), Algorithms Design (3302/3326)}{}{}
	
	
	\section*{Publications}
	
	\subsection*{International Conferences}
	
	\cventry{2024}{An Empirical Study on the Suitability of Test-based Patch Acceptance Criteria.}{Luciano Zemín, Ariel Godio, César Cornejo, Renzo Degiovanni, Simón Gutiérrez Brida, Germán Regis, Nazareno Aguirre, Marcelo Frias}{Accepted for publication at ACM Transactions on Software Engineering and Methodology (TOSEM)}{}{Full Research Paper. (Q1 Scimago)}
	
	\cventry{2024}{An Analysis of the Impact of Field-Value Instance Navigation in Alloy's Model Finding.}{César Cornejo, María Marta Novaira, Sonia Permigiani, Nazareno Aguirre, Marcelo F. Frias, Simón Gutiérrez Brida, Germán Regis}{Rigorous State-Based Methods - 10th International Conference. (ABZ 2024)}{Bergamo, Italy}{Full Research Paper. (B2 Qualis)}
	
	\cventry{2022}{ICEBAR: Feedback-Driven Iterative Repair of Alloy Specifications.}{Simón Gutiérrez Brida, Germán Regis, Guolong Zheng, Hamid Bagheri, ThanhVu Nguyen, Nazareno Aguirre, Marcelo F. Frias}{37th International Conference on Automated Software Engineering. (ASE 2022)}{Michigan, US}{Full Research Paper. (A1 Qualis)}
	
	\cventry{2022}{ATR: template-based repair for Alloy specifications.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{31st International Symposium on Software Testing and Analysis (ISSTA 2022)}{Virtual, South Korea}{Full Research Paper. (A2 Qualis)}
	
	\cventry{2021}{FLACK: Localizing Faults in Alloy Models.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{36th International Conference on Automated Software Engineering (ASE 2021)}{Melbourne, Australia}{Tool Paper. (A1 Qualis)}
	
	\cventry{2021}{BeAFix: An Automated Repair Tool for Faulty Alloy Models.}{Simón Gutiérrez Brida, Germán Regis, Guolong Zheng, Hamid Bagheri, ThanhVu Nguyen, Nazareno Aguirre, Marcelo F. Frias}{36th International Conference on Automated Software Engineering (ASE 2021)}{Melbourne, Australia}{Tool Paper. (A1 Qualis)}
	
	\cventry{2021}{Artifact of 'FLACK: Counterexample-Guided Fault Localization for Alloy Models'.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Artifact Paper.}
	
	\cventry{2021}{FLACK: Counterexample-Guided Fault Localization for Alloy Models.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Full Research Paper. (A1 Qualis)}
	
	\cventry{2021}{Artifact of Bounded Exhaustive Search of Alloy Specification Repairs.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Artifact Paper.}
	
	\cventry{2021}{Bounded Exhaustive Search of Alloy Specification Repairs.}{Simón Gutiérrez Brida, Germán Regis, Guolong Zheng, Hamid Bagheri, ThanhVu Nguyen, Nazareno Aguirre, Marcelo F. Frias}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Full Research Paper. (A1 Qualis)}
	
	\cventry{2019}{On the effect of object redundancy elimination in randomly testing collection classes.}{P. Ponzio, V. Bengolea, S. Guti\'errez Brida, G. Scilingo, N. Aguirre, M. Frias}{11th International Workshop on Search-Based Software Testing (SBST 2018)}{Gothenburg, Sweden}{Full Research Paper.}
	
	\cventry{2017}{An Analysis of the Suitability of Test-based Patch Acceptance Criteria}{L. Zem\'in, S. Guti\'errez, A. Godio, C. Cornejo, R. Degiovanni, G. Regis, N. Aguirre and M. Frias}{10th International Workshop on Search-Based Software Testing (SBST 2017)}{Buenos Aires, Argentina}{Full Research Paper.}
	
	\cventry{2017}{Boolean expression extender - A mutation operator for strengthening and weakening boolean expressions}{S. Guti\'errez Brida, G. Scilingo}{2017 XLIII Latin American Computer Conference (CLEI 2017)}{C\'ordoba, Argentina}{Full Research Paper. (B4 Qualis)}
	
	\cventry{2017}{DynAlloy Analyzer: A Tool for the Specification and Analysis of Alloy Models with Dynamic Behaviour}{G. Regis, C. Cornejo, S. Guti\'errez Brida, M. Politano, F. Raverta, P. Ponzio, N. Aguirre, J.P. Galeotti, M. Frias}{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering (ESEC/FSE 2017)}{Paderborn, Alemania}{Tool Paper. (A2 Qualis)}
	
	\subsection*{National Conferences}
	
	\cventry{2019}{Detecci\'on de objetos espurios en generaci\'on autom\'atica de entradas}{Sim\'on Guti\'errez Brida, Pablo Ponzio, Valeria Bengolea, y Nazareno Aguirre}{en Congreso Argentino de Ciencias de la Computaci\'on 2019 (CACIC 2019)}{R\'io Cuarto, Argentina}{}
	
	\cventry{2019}{Implementaci\'on B\'asica de Typestates en Rust}{Marcelo Arroyo, Sim\'on Guti\'errez Brida, Pablo Ponzio}{en Congreso Argentino de Ciencias de la Computaci\'on 2019 (CACIC 2019)}{R\'io Cuarto, Argentina}{}
	
	\cventry{2012}{Criterios de Cobertura sobre RepOK para Reducir Test Suites Exhaustivas Acotadas: Estudio de Casos}{V. Bengolea, S. Guti\'errez Brida y N. Aguirre}{en Congreso Argentino de Ciencias de la Computaci\'on 2012 (CACIC 2012)}{Bah\'ia Blanca, Argentina}{}
	
	\section*{Article Evaluation}
	\subsection*{International Conferences}
	\cventry{2022}{FSE/ESEC 2022 Artifacts Track}{Evaluation of two Artifact submissions}{}{}{}
	
	\subsection*{National and Regional Conferences}
	\cventry{2019}{SLISW 2019}{Evaluation of un article in Conferencia Latinoamericana de Informática}{}{}{}
	
	\cventry{2017}{SLISW 2017}{Evaluation if two articles in Conferencia Latinoamericana de Informática}{}{}{}
	
	\cventry{2017}{ASSE 2017}{Evaluation of two articles in Conferencia Latinoamericana de Informática}{}{}{}
	
	\section*{Undergrad Thesis Supervision}
	
	\cventry{2017 - 2019}{Leandro Buttignol.}{Comparison of Automatic test generation tools.}{}{Co-supervised with Pablo Ponzio (Supervisor), and Valeria Bengolea (Co-Supervisor)}{}{}
	
	\section*{Evaluation Committees Participation}
	
	\subsection*{Student Teaching Assistant}
	\cventry{2012}{In student teaching assistant selection for Computer Science Department.}{}{}{Universidad Nacional de Río Cuarto, Córdoba, Argentina.}{}
	
	\section*{Attendance to Scientific Meetings}
	\cventry{2021}{ICSE 2021}{}{43rd International Conference on Software Engineering, Madrid, Spain}{}{}
	\cventry{2017}{ICSE 2017}{}{39th International Conference on Software Engineering, Buenos Aires, Argentina}{}{}
	\cventry{2014}{JAIIO/CLEI 2017}{}{46 Jornadas Argentinas de Inform\'atica / 43 Conferencia Latinoamericana de Inform\'atica, Universidad Tecnol\'ogica Nacional, C\'ordoba, Argentina}{}{}
	\cventry{2008-2019}{Computer Science Summer School RIO}{}{editions 2008, 2009, 2010, 2011, 2012, 2013, 2015, 2016, 2017, 2018, 2019, y 2020}{Computer Science Deptarment, Universidad Nacional de Río Cuarto}{}
	
	\section*{Administrative positions}
	
	\cventry{2017-2022}{Member of Computer Science department council in representation of graduate students.}{}{Departamento de Computaci\'on de la Universidad Nacional de R\'io Cuarto.}{}{}
	
	\section*{Scientific-Technological events participation and organization}
	\cventry{2016-2020}{Computer Science Summer School RIO}{Universidad Nacional de Río Cuarto}{Member of organizing committee}{}{}
	
	\cventry{2017}{ICSE 2017 39th International Conference on Software Engineering}{Buenos Aires, Argentina}{Student Volunteer}{}{}
	
\end{document}