\documentclass[11pt,a4paper]{moderncv}

\usepackage{enumitem}
% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[T1]{fontenc}
\usepackage{lmodern}
% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage[english]{babel}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\footnotesize } % other info in "inner" position of footer line

%number is section
%\newcounter{secnumber}
%\renewcommand\sectionstyle[1]{{%
		%  \refstepcounter{secnumber}%
		%  \sectionfont
		%  \textcolor{color1}{\thesecnumber~#1}%
		%}}

% personal data
\firstname{\Huge Simón Emmanuel}
\familyname{Gutiérrez Brida}
\title{Curriculum Vitae} 
%\address{<Address Street>}{<Addres Place>}
\mobile{+549 (358) 4396 444}
\phone{+549 (358) 4676 235}
%\fax{<Fax number>}
\email{sgutierrez@dc.exa.unrc.edu.ar}
\homepage{http://saiema.github.io/}
\social[orcid]{0000-0003-3115-2739}

%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[100pt]{pict.JPG}
%\photo[84pt]{foto.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"Success is the ability to go from failure to failure without losing your enthusiasm." -- Winston Churchill}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{wasysym}

\begin{document}
	\maketitle
	
	\section*{Información Personal}
	\begin{minipage}{9cm}
		\begin{itemize}
			\item Ciudad: Río Cuarto, Córdoba
			\item Fecha de Nacimiento: 14/10/1983
			\item Lugar de Nacimiento: Ciudad de Buenos Aires
		\end{itemize}
	\end{minipage}
	
	\section*{Actividades actuales}
	\cventry{}{}{}{}{}{Actualmente me desempeño como Jefe de Trabajos Prácticos con dedicación Simple en el Departamento de Computación de la Universidad Nacional de Río Cuarto. Mi área de investigación se centra en la calidad de software, haciendo incapié en generación y evaluación de tests; reparación automática de programas; y especificaciones formales.}
	
	\section*{Estudios Realizados}
	\cventry{2014-2019}{Doctorado en Ciencias de la Computación}{}{FAMAF, UNC}{Córdoba}{}
	\cventry{2009-2014}{Licenciatura en Ciencias de la Computación}{}{UNRC}{Río Cuarto}{}
	\cventry{2007-2011}{Analista en Computación}{}{UNRC}{Río Cuarto}{}
	
	
	\section{Becas Obtenidas}
	\cventry{2019-2021}{Beca de Posdoctorado}{}{Otorgada por CONICET}{}{}
	\cventry{2014-2019}{Beca interna Doctoral}{}{Otorgada por CONICET}{}{}
	\cventry{2012}{Becas de Fin de Carrera para Estudiantes de Grado en Carreras TICs}{}{Otorgada por ANPCYT}{}{}
	\cventry{2011}{Beca de Estímulo a las Vocaciones Científicas.}{}{Otorgada por CIN}{}{}
	
	\section*{Proyectos de investigación}
	
	\subsection*{Proyectos de investigación financiados}
	\cventry{2019}{Improving software testing through automatic translation of test inputs to API calls.}{Otorgado por Ministerio de Ciencia y Tecnología.}{}{}{}
	
	\subsection*{Colaborador en proyectos de investigación}
	\cventry{2016-2018}{Formal methods for Software Specification, Design, and Verification.}{PPI}{Otorgado por la Secretaria de Ciencia y Técnica, Universidad Nacional de Río Cuarto}{Director de proyecto: Dr. Nazareno Aguirre}{}
	
	\cventry{2012-2015}{Formal methods for Software Specification, Design, and Verification.}{PPI}{Otorgado por la Secretaria de Ciencia y Técnica, Universidad Nacional de Río Cuarto}{Director de proyecto: Dr. Nazareno Aguirre}{}
	
	\section*{Docencia}
	
	\cventry{Febreo 2024- Agosto 2024}{Jefe de Trabajos Prácticos con dedicación simple}{}{Departamento de Computación en Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{Marzo 2023- Marzo 2024}{Profesor}{Guangdong Technion-Israel Institute of Technology}{Shantou, Provincia de Guangdong, China}{}{}
	
	\cventry{Abril 2019- Febrero 2023}{Ayudante de Primera con dedicación Simple}{}{Departamento de Computación en Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{Abril 2018- Diciembre 2018}{Ayudante de Primera con dedicación Simple}{}{Departamento de Computación en Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{Agosto 2015- Marzo 2017}{Ayudante de Primera con dedicación Simple}{}{Departamento de Computación en Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	\cventry{2008-2012}{Ayudante de Segunda}{}{Departamento de Computación en Universidad Nacional de Río Cuarto, Río Cuarto, Córdoba, Argentina.}{}{}
	
	
	\section*{Publicaciones}
	
	\subsection*{Conferencias Internacionales}
	\cventry{2022}{ICEBAR: Feedback-Driven Iterative Repair of Alloy Specifications.}{Simón Gutiérrez Brida, Germán Regis, Guolong Zheng, Hamid Bagheri, ThanhVu Nguyen, Nazareno Aguirre, Marcelo F. Frias}{37th International Conference on Automated Software Engineering. (ASE 2022)}{Michigan, US}{Full Research Paper. (A1 Qualis)}
	
	\cventry{2022}{ATR: template-based repair for Alloy specifications.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{31st International Symposium on Software Testing and Analysis (ISSTA 2022)}{Virtual, South Korea}{Full Research Paper. (A2 Qualis)}
	
	\cventry{2021}{FLACK: Localizing Faults in Alloy Models.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{36th International Conference on Automated Software Engineering (ASE 2021)}{Melbourne, Australia}{Tool Paper. (A1 Qualis)}
	
	\cventry{2021}{BeAFix: An Automated Repair Tool for Faulty Alloy Models.}{Simón Gutiérrez Brida, Germán Regis, Guolong Zheng, Hamid Bagheri, ThanhVu Nguyen, Nazareno Aguirre, Marcelo F. Frias}{36th International Conference on Automated Software Engineering (ASE 2021)}{Melbourne, Australia}{Tool Paper. (A1 Qualis)}
	
	%\cventry{2021}{Artifact of FLACK: Counterexample-Guided Fault Localization for Alloy Models.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Artifact Paper.}
	
	\cventry{2021}{FLACK: Counterexample-Guided Fault Localization for Alloy Models.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Full Research Paper. (A1 Qualis)}
	
	%\cventry{2021}{Artifact of Bounded Exhaustive Search of Alloy Specification Repairs.}{Guolong Zheng, ThanhVu Nguyen, Simón Gutiérrez Brida, Germán Regis, Marcelo F. Frias, Nazareno Aguirre, Hamid Bagheri}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Artifact Paper.}
	
	\cventry{2021}{Bounded Exhaustive Search of Alloy Specification Repairs.}{Simón Gutiérrez Brida, Germán Regis, Guolong Zheng, Hamid Bagheri, ThanhVu Nguyen, Nazareno Aguirre, Marcelo F. Frias}{43rd International Conference on Software Engineering (ICSE 2021)}{Madrid, Spain}{Full Research Paper. (A1 Qualis)}
	
	\cventry{2019}{On the effect of object redundancy elimination in randomly testing collection classes.}{P. Ponzio, V. Bengolea, S. Gutiérrez Brida, G. Scilingo, N. Aguirre, M. Frias}{11th International Workshop on Search-Based Software Testing (SBST 2018)}{Gothenburg, Sweden}{Full Research Paper.}
	
	\cventry{2017}{An Analysis of the Suitability of Test-based Patch Acceptance Criteria}{L. Zemín, S. Gutiérrez, A. Godio, C. Cornejo, R. Degiovanni, G. Regis, N. Aguirre and M. Frias}{10th International Workshop on Search-Based Software Testing (SBST 2017)}{Buenos Aires, Argentina}{Full Research Paper.}
	
	\cventry{2017}{Boolean expression extender - A mutation operator for strengthening and weakening boolean expressions}{S. Gutiérrez Brida, G. Scilingo}{2017 XLIII Latin American Computer Conference (CLEI 2017)}{Córdoba, Argentina}{Full Research Paper. (B4 Qualis)}
	
	\cventry{2017}{DynAlloy Analyzer: A Tool for the Specification and Analysis of Alloy Models with Dynamic Behaviour}{G. Regis, C. Cornejo, S. Gutiérrez Brida, M. Politano, F. Raverta, P. Ponzio, N. Aguirre, J.P. Galeotti, M. Frias}{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering (ESEC/FSE 2017)}{Paderborn, Alemania}{Tool Paper. (A2 Qualis)}
	
	\subsection*{Conferencias Nacionales}
	
	\cventry{2019}{Detección de objetos espurios en generación automática de entradas}{Simón Gutiérrez Brida, Pablo Ponzio, Valeria Bengolea, y Nazareno Aguirre}{en Congreso Argentino de Ciencias de la Computación 2019 (CACIC 2019)}{Río Cuarto, Argentina}{}
	
	\cventry{2019}{Implementación Básica de Typestates en Rust}{Marcelo Arroyo, Simón Gutiérrez Brida, Pablo Ponzio}{en Congreso Argentino de Ciencias de la Computación 2019 (CACIC 2019)}{Río Cuarto, Argentina}{}
	
	\cventry{2012}{Criterios de Cobertura sobre RepOK para Reducir Test Suites Exhaustivas Acotadas: Estudio de Casos}{V. Bengolea, S. Gutiérrez Brida y N. Aguirre}{en Congreso Argentino de Ciencias de la Computación 2012 (CACIC 2012)}{Bahía Blanca, Argentina}{}
	
	\section*{Evaluación de Artículos}
	\subsection*{Conferencias Internacionales}
	\cventry{2022}{FSE/ESEC 2022 Artifacts Track}{Evaluación de dos publicaciones de artefactos}{}{}{}
	
	\subsection*{Conferencias Nacionales y Regionales}
	\cventry{2019}{SLISW 2019}{Evaluación de un artículo en Conferencia Latinoamericana de Informática}{}{}{}
	
	\cventry{2017}{SLISW 2017}{Evaluación de dos artículos en Conferencia Latinoamericana de Informática}{}{}{}
	
	\cventry{2017}{ASSE 2017}{Evaluación de dos artículos en Conferencia Latinoamericana de Informática}{}{}{}
	
	\section*{Supervisión de Tesis de Grado}
	
	\cventry{2017 - 2019}{Leandro Buttignol.}{Comparison of Automatic test generation tools.}{}{Co-supervisado con Pablo Ponzio (Supervisor), y Valeria Bengolea (Co-Supervisora)}{}{}
	
	\section*{Participación y organización en eventos Científico-Tecnológicos}
	\cventry{2016-2020}{Escuela de Verano de Ciencias de la Computación (RIO)}{Universidad Nacional de Río Cuarto}{Miembro del comité organizador}{}{}
	
	\cventry{2017}{ICSE 2017 39th International Conference on Software Engineering}{Buenos Aires, Argentina}{Estudiante Voluntario}{}{}
	
	\section*{Tareas Académicas de Gestión/Administrativas}
	
	\cventry{Diciembre 2017- Agosto 2022}{Integrante Graduado del Consejo Departamental}{}{en el Dpto. Computación de la UNRC}{2 períodos titular, uno suplente}{}
	
\end{document}